---
title: ""
author: ""
date: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(xts)
library(ggplot2)
library(fasttime) #for fastPosixct
Sys.setenv(TZ="Asia/Kolkata")
library(scales)
library(plotly)
library(knitr)
```
The data used in the analysis is presented in below tabular format

```{r maincode, echo=FALSE}
energydata <- "/Volumes/MacintoshHD2/Users/haroonr/Detailed_datasets/aravali_iitb/year2016_data/hourly/onlyservyed_flats.csv"
df <- fread(energydata)
dfs <-  xts(df[,2:dim(df)[2]],fastPOSIXct(df$timestamp)-19800)

bill_array <- vector()
for( h in 1:dim(dfs)[2])
{
dat_flat <-  dfs[,h]
monthwise <- split.xts(dat_flat,f="months",k=1)
#meanenergy <- sapply(monthwise,mean,na.rm=TRUE)
sumenergy <- sapply(monthwise,sum,na.rm=TRUE)
#avg_monthunits <- (meanenergy*24*30)/1000
sum_monthunits <- sumenergy/1000
unit <- mean(sum_monthunits[2:length(sum_monthunits)]) # excluding june month

if(unit <= 30)
  { amt <- unit * 0.6
} else if(unit <= 100){
  amt <- 18 + (unit-30)*0.9
} else if(unit <= 150){
  amt <- 18 + 63 + (unit-100)*1.1
} else if(unit <= 200){
  amt <- 18 + 63 + 55 + (unit-150)*1.3
} else if(unit <= 300){
  amt <- 18 + 63 + 55 + 65 + (unit-200)*1.3
}else{
  amt <- 18 + 63 + 55 + 65 + 130 + (unit-300)*1.35
}
x = (unit) * (0.1283 - 0.4405 + 0.0904)
y = amt * 5.81
z =  40
billamt <- round(x+y+z)
#pos <- length(bill_array)+1
bill_array[h] <- billamt
}
#bill_frame <- data.frame(flat = colnames(dfs),actual= bill_array)
names(bill_array) <- colnames(dfs) 

surfile <- "/Volumes/MacintoshHD2/Users/haroonr/Detailed_datasets/aravali_iitb/surveydata.csv"
sfile <- read.csv(surfile)
sframe <- sfile[,c(8,10)]
sframe$flatId <- paste0('F',actual_bill=sframe$flatId)

labnames <- c("lessthan500","500to1000","1001to1500","1501to2000","Above2000","dontknow")
sframe$avgBill <- factor(sframe$avgBill,levels=labnames,labels=labnames)
sframe$reportedBillrange <- as.numeric(sframe$avgBill)
sframe$actualBill <- bill_array[sframe$flatId]

actual_bill_range <- vector()
for(k in 1:length(sframe$actualBill))
{ val <- sframe$actualBill[k]
  if(is.na(val)) {
  actual_bill_range[k] <- NA
  } else{
  if(val < 500) {
    actual_bill_range[k] <- 1
  } else if(val < 1000){
    actual_bill_range[k] <- 2
  } else if(val < 1500){
    actual_bill_range[k] <- 3
  } else if(val < 2000){
    actual_bill_range[k] <- 4
  } else {
    actual_bill_range[k] <- 5
  }
  }
}
sframe$actualBillrange <- actual_bill_range
lframe <- sframe[!is.na(sframe$actualBillrange),]
```

```{r kable,echo=FALSE}
colnames(lframe) <- c("flatId","reportedBill","reportedBillrange","actualBill","actualBillrange")
kable(lframe)
#kable(table(lframe$reportedBillrange==lframe$actualBillrange))
```

The average bill amount is 
```{r bill, echo=FALSE}
mean(lframe$actualBill)
```

On comparing columns, "reportedBillrange" and "actualBillrange", we found

```{r kablefunction,echo=FALSE}
l <- table(lframe$reportedBillrange==lframe$actualBillrange)
print(l)
```
This means 16 consumers know correctly how much they are charged. Out of 25 consumers who answered wrongly, 5 consumers responded that they "don't know". In conclusion, 16 consumers answered correctly and 20 (25-5) answered wrongly. 